COMPAS Race Analysis

### 2022-03-30 race compas analysis.Rmd
testing fairness metrics code

print(f'[Baseline] The statistical parity difference is {stat_par_diff: .2}')
```

@@

print(f'[Baseline] The equal opportunity difference is {eq_opp_diff: .2}')
```

>>>>

print(f'[Baseline] The statistical parity difference is {stat_par_diff: .2}')

disp_impact_ratio = disparate_impact_ratio(y_test, y_pred, prot_attr='race', pos_label = 0)

print(f'[Baseline] The disparate impact ratio is {disp_impact_ratio: .2}')
# disparate impact ratio without y_pred attribute was 0.77

avg_odds_error = average_odds_error(y_test, y_pred, prot_attr='race', pos_label = 0)

print(f'[Baseline] The average odds error is {avg_odds_error: .2}')

avg_odds_diff = average_odds_difference(y_test, y_pred, prot_attr='race', pos_label = 0)

print(f'[Baseline] The average odds difference is {avg_odds_diff: .2}')
```

@@

print(f'[Baseline] The equal opportunity difference is {eq_opp_diff: .2}')

#bt_grp_gen_entr_error = between_group_generalized_entropy_error(y_test, y_pred, alpha=1, pos_label = 0)

#print(f'[Baseline] The between group generalized entropy error is {bt_grp_gen_entr_error: .2}')

#gen_entr_index = generalized_entropy_index(x_test, alpha=0, pos_label = 0)

#print(f'[Baseline] The generalized entropy index is {gen_entr_index: .2}')

#consistency_score = consistency_score(x_test, y_test, n_neighbors=5, pos_label = 0)

#print(f'[Baseline] The consistency score is {consistency_score: .2}')
```
